### 2018-07-09 FrascatiPlot/Paper/NucleiB2.tex
starting to write chapter 4.2

 \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
 - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!

>>>>

 \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}

In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation tuned to the data is used. The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}. For deuterons and \hethree\ both approaches lead to similar to similar predictions and give a reasonable description of the experimental data.

 - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!
